Avoiding tipping points in fisheries management through Gaussian Process Dynamic Programming

### 2014-11-11 manuscripts/manuscript.tex

We use a Metropolis-Hastings Markov Chain Monte Carlo (Gelman et al.
(2003)) to infer posterior distributions of the parameters of the GP
(Figure S3, code in appendix). Since the posterior distributions differ
substantially from the priors (Figure S3), most of the information in
the posterior comes from the data rather than the prior belief.

>>>>

We use a Metropolis-Hastings Markov Chain Monte Carlo (Gelman et al.
(2003)) to infer posterior distributions of the parameters of the GP
(Figure S4, code in appendix). Since the posterior distributions differ
substantially from the priors (Figure S4), most of the information in
the posterior comes from the data rather than the prior belief.
